# Tidy manipulations and grouping operations

## Getting the data

Get the `SAFI_clean.csv` dataset, which you can read about and **download** from here: https://figshare.com/articles/SAFI_Survey_Results/6262019.

We will use the "tidyverse" of packages for this:

```{r}    
## load the tidyverse
library(tidyverse)

interviews <- read_csv("C:/Users/ZHENLIU/Documents/2019LSEmodules/DScode/week5classpractice/class5/SAFI_clean.csv", na = "NULL")

## inspect the data
interviews

## preview the data
View(interviews)
```

## Creating new variables

Create a new variable which is thse number of people per room.  

Compute a median of the number of people per room, for each village.

Extra: Produce a boxplot of the number of people per room, by village.
```{r}    
## create a new varaible 
interviews$ppr <- interviews$no_membrs/interviews$rooms

q1<- aggregate(interviews$ppr, list(interviews$village), median)
q1

boxplot(ppr~village, interviews, xlab = "name of the village",
   ylab = "number of people per room", main= "number of people per room in each village")   
    
```
